Kernel Phase and Coronagraphy with Automatic Differentiation

### 2020-05-28 ms.tex

We now consider a very simple Lyot coronagraph \citep{lyot30}, using \textsc{morphine}. We choose a 1\,$\mu$m wavelength, and 1\,m diameter pupil sampled on a $64\times64$ grid. The central $4 \lambda/D$ region of the resulting PSF is blocked out with a focal plane stop, and the light is then propagated to a second pupil plane using an FFT rather than a matrix FT, following standard \textsc{poppy} practice; this imposes tougher memory constraints, and in future may be replaced with an MFT. A Lyot stop (a pupil mask undersized 10\% relative to the input pupil) is then imposed, and the light is propagated to a final focal plane sampled on a 50\,mas pixel scale grid with a 4~arcsec field of view. Aside from the coarse gridding, this is intentionally identical to one of the standard example pieces for \textsc{poppy}\footnote{\href{https://github.com/mperrin/poppy/blob/master/notebooks/MatrixFTCoronagraph_demo.ipynb}{github.com/mperrin/poppy/blob/master/notebooks/MatrixFTCoronagraph\_demo.ipynb}}, for the sake of consistency. The PSF produced has a dark coronagraphic hole in the middle, and beyond an inner working angle around this hole has a nearly normal Airy pattern of diffraction rings.

@@

Calculating the SVD of this Jacobian (again restricted to the support of the primary pupil) we se that unlike in the case of the simple diffraction, there is not a sharp cliff but instead a rolling-off which nevertheless reaches very small singular values. The singular value curve is displayed in Figure~\ref{fig:svd} in orange.

@@

>>>>

We now consider a very simple Lyot coronagraph \citep{lyot30}, using \textsc{morphine}. We choose a 1\,$\mu$m wavelength, and 1\,m diameter pupil sampled on a $96\times96$ grid. The central $4 \lambda/D$ region of the resulting PSF is blocked out with a focal plane stop, and the light is then propagated to a second pupil plane using an FFT rather than a matrix FT, following standard \textsc{poppy} practice; this imposes tougher memory constraints, and in future may be replaced with an MFT. A Lyot stop (an iris mask undersized 10\% relative to the input pupil) is then imposed, and the light is propagated to a final focal plane sampled on a 50\,mas pixel scale grid with a 4~arcsec field of view. Aside from the coarse gridding, this is intentionally identical to one of the standard example pieces for \textsc{poppy}\footnote{\href{https://github.com/mperrin/poppy/blob/master/notebooks/MatrixFTCoronagraph_demo.ipynb}{github.com/mperrin/poppy/blob/master/notebooks/MatrixFTCoronagraph\_demo.ipynb}}, for the sake of consistency. The PSF produced has a dark coronagraphic hole in the middle, and beyond an inner working angle around this hole has a nearly normal Airy pattern of diffraction rings.

@@

Calculating the SVD of this Jacobian (again restricted to the support of the primary pupil) we se that unlike in the case of the simple diffraction, there is not a sharp cliff but instead a rolling-off which nevertheless reaches very small singular values. The singular value curve is displayed in Figure~\ref{fig:svd_coronagraph}.

@@

\begin{figure}
    \plotone{corona_singular.pdf}
     \caption{Log-scale plot of the singular values of the phase transfer matrix versus index for the coronagraph simulation in Section~\ref{sec:coronagraph}. Singular values are normalized to the first singular value.}
    \label{fig:svd_coronagraph}
\end{figure}
